---
title: "Homework-2 | Computing sentiment"
author: "Szymon Talaga, Mikołaj Biesaga, ISS UW"
output:
  html_notebook:
    toc: true
---

```{r global_options, include = FALSE}
# Do not bother with this chunk because it only defines some visual options for other chunks
knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE, include = TRUE, fig.align = "center", fig.height = 3, fig.width = 3
)
```

## Load packages

```{r load_packages}
## Load packages needed in this script
library(rtweet) # for downloading data from Twitter
library(dplyr) # for data transformation
library(magrittr) # for data transformation
library(tidytext) # for text analysing
library(stringr) # for dealing with strings
library(wordcloud) # for basic text visualisation
library(ggplot2) # for graphics
library(DataCombine) # for data transformation
library(reshape2) # for data transformation
library(tidyr) # for data transformation
library(igraph) # for creating graphs
library(ggraph) # for creating graphs
library(widyr) # for ngrams statistics
library(lubridate) # for date transformation
library(feather) # for very light data format
library(PMCMRplus) # for post hoc kruskal-walis test
library(scales) # for scales
source("clean_twitter_data.R") # load our custom cleaning function
data("stop_words") # load data frame with stop words.
```

## How to submit the Homework

Please submit two files `Rmd` file with your homework and your original data set in `csv` format.

## General Hint

This time this is a lot of work but it should be quite simple copy and paste, however probably a bit annoying. The reason I want you to repeat all of this yourself without much of hints is that I want you to face problems when I am here to help not when I am away.

## Aggregate sentiment

Use the data from `Homework2.Rmd` and aggregate sentiment by tweets.

```{r agrregate}
Homework2_3 <- read_csv2("Homework2_2.csv") %>%
  NULL ## replace NULL with solution, otherwise it returns error.
```

## Get timelines

Download timelines of at least three accounts of your choice. You need to get at least 1000 tweets from each. The more different accounts, the better.

```{r get_timelines}
Homework3 <- NULL ## replace NULL with solution, otherwise it returns error.

## Save to csv
Homework3 %>%
  save_as_csv("Homework3.csv")
```

## Clean and transform the data

Prepare the data set for computing tf-idf statistics.

```{r transform_data}

```

## Create a dictionary

Create a dictionary.

```{r create_dictionary}

```

<!-- CSS styling -->
<style>
    html {
        height: 100%;
        font-size: 62.5%;
    }
    body {
        text-align: justify;
        height: 100%;
        font-size: 1.6em;
        font-family: "Trebuchet MS", "Lucida Grande", "Lucida Sans Unicode", "Lucida Sans", sans-serif;
    }
    h1, h2, h3 {
        text-align: center;
    }
    h4.author, h4.date {
        margin: 0.75em 0 0 0;
        text-align: center;
    }
    h2, h3, h4, h5, h6 {
        margin: 2em 0 1em 0;
    }
    div#header {
        margin: 1em 0 1em 0;
    }
    hr {
        margin: 2em 0 2em 0;
    }
    pre {
        margin-bottom: 2em;
    }
</style>