---
title: "Homework-3 | Creating dictionary"
author: "Szymon Talaga, Mikołaj Biesaga, ISS UW"
output:
  html_notebook:
    toc: true
---

```{r global_options, include = FALSE}
# Do not bother with this chunk because it only defines some visual options for other chunks
knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE, include = TRUE, fig.align = "center", fig.height = 3, fig.width = 3
)
```

## Load packages

```{r load_packages}
## Load packages needed in this script
library(rtweet) # for downloading data from Twitter
library(dplyr) # for data transformation
library(magrittr) # for data transformation
library(tidytext) # for text analysing
library(stringr) # for dealing with strings
library(wordcloud) # for basic text visualisation
library(ggplot2) # for graphics
library(DataCombine) # for data transformation
library(reshape2) # for data transformation
library(tidyr) # for data transformation
library(igraph) # for creating graphs
library(ggraph) # for creating graphs
library(widyr) # for ngrams statistics
library(lubridate) # for date transformation
library(feather) # for very light data format
library(PMCMRplus) # for post hoc kruskal-walis test
library(scales) # for scales
source("clean_twitter_data.R") # load our custom cleaning function
```

## How to submit the Homework

Please submit two files `Rmd` file with your homework and your original data set in `csv` format. In other words Homework3.Rmd and Homework3.tweets.csv.

## General Hint

This time this is a lot of work but it should be quite simple copy and paste, however probably a bit annoying. The reason I want you to repeat all of this yourself without much of hints is that I want you to face problems when I am here to help not when I am away.

## Get timelines

Download timelines of at least three accounts of your choice. You need to get at least 1000 tweets from each. The more different accounts, the better.
*Solution:* It should be fairly straightforward. The only thing you need to be careful about is to copy the screen names correctly.

```{r get_timelines}
accounts <- c("ManUtd","ManCity","LFC","SpursOfficial")
Homework3 <- get_timelines(accounts,n=1000)

## Save to csv. It will create two files one Homework3.tweets.csv and other Homework3.users.csv
Homework3 %>%
  save_as_csv("Homework3.csv")
```

## Clean and transform the data

Prepare the data set for computing tf-idf statistics.

*Solution:* First, you need to compute word frequency by screen name and afterwards total number of words. It is redundant to what we did on Wednesday. The only thing which I skipped was deleting stop words because anyway they are deleted.

```{r transform_data}
## Compute total number of words in each category
Homework3_words <- read_twitter_csv("Homework3.tweets.csv") %>%
  ## Change from wide format to long. Now word is a record
  unnest_tokens(input=text,
                output=word) %>%
  ## Count words in each category
  count(screen_name,word,sort=TRUE) %>%
  ## Unroup because the previous function by defualt leaves the data set grouped
  ungroup() %>%
  ## Group by categories
  group_by(screen_name) %>%
  ## Count words in each category
  summarise(total=sum(n))

## Add total number of words to word frequency
Homework3_counts <- read_twitter_csv("Homework3.tweets.csv") %>%
  ## Change from wide format to long. Now word is a record
  unnest_tokens(input=text,
                output=word) %>%
  ## Count words frequency in each category
  count(screen_name,word,sort=TRUE) %>%
  ## Ungroup
  ungroup() %>%
  ## Join total number of words
  left_join(Homework3_words)

```

## Create a dictionary

Create a dictionary.

*Solution:* It is just copy paste from `Twitter-3.Rmd`. The only difference is that it is even less interesting than beofore. If you know anything about football (sorry, soccer) you easily realise that all the items in this dictioanry are either names of players or hashtags about games. Therefore, it is kind of useless...

```{r create_dictionary}
## Compute tf-idf
Homework3_tf_idf <- Homework3_counts %>%
  bind_tf_idf(word, screen_name, n)

## Create the dictioanry
Homework3_dictionary <- Homework3_tf_idf %>%
  ## Filter only terms which appear in one of the dictionaries
  filter(idf==max(idf)) %>%
  ## Select only two categories
  select(screen_name, word)
```

<!-- CSS styling -->
<style>
    html {
        height: 100%;
        font-size: 62.5%;
    }
    body {
        text-align: justify;
        height: 100%;
        font-size: 1.6em;
        font-family: "Trebuchet MS", "Lucida Grande", "Lucida Sans Unicode", "Lucida Sans", sans-serif;
    }
    h1, h2, h3 {
        text-align: center;
    }
    h4.author, h4.date {
        margin: 0.75em 0 0 0;
        text-align: center;
    }
    h2, h3, h4, h5, h6 {
        margin: 2em 0 1em 0;
    }
    div#header {
        margin: 1em 0 1em 0;
    }
    hr {
        margin: 2em 0 2em 0;
    }
    pre {
        margin-bottom: 2em;
    }
</style>