---
title: "Homework-2 | Computing sentiment"
author: "Szymon Talaga, Mikołaj Biesaga, ISS UW"
output:
  html_notebook:
    toc: true
---

```{r global_options, include = FALSE}
# Do not bother with this chunk because it only defines some visual options for other chunks
knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE, include = TRUE, fig.align = "center", fig.height = 3, fig.width = 3
)
```

```{r load_packages}
## Load packages needed in this script
library(rtweet) # for downloading data from Twitter
library(dplyr) # for data transformation
library(magrittr) # for data transformation
library(tidytext) # for text analysing
library(stringr) # for dealing with strings
library(wordcloud) # for basic text visualisation
library(ggplot2) # for graphics
library(DataCombine) # for data transformation
library(reshape2) # for data transformation
library(lubridate) # had to add this package for date manegment
```
## How to submit the Homework

Please submit two files `Rmd` file with your homework and your original data set in `csv` format.

## General Hint

One of the most important things when you are coding is to name variables or files with proper names. Try to avoid using single letters or acronyms because they are confusing and you will forget what they stand for the moment you check your Facebook. If there is an error with loading a file double or triple check if it really is called like you think it is.

## Transform data

Take the data set from Homework 1 and perform following operation on it.

* Select columns: text, created_at, screen_name, source, status_id, favorite_count, retweet_count, hashtags
* Translate emojis, and delete the untranslatable ones
* Delete words used in the query
* Get rid of links from tweets
* Split words into stems
* Delete rows with stop words

*Hint:* Read carefully what you are supposed to do and `Twitter-1.Rmd`

*Solution:* It should be more or less straightforward because it was just about copying and pasting the code from `Twitter-2.Rmd`. The only thing which had to be changed was swapping `status_id` column with `screen_name` which are more or less the same.

```{r transfomr_data}
data("emojis")
emojis <- emojis %>%
  mutate(code=iconv(code,from="latin1",to="ascii",sub="byte")) %>%
  mutate(description=paste0(" ",description," ")) 

Homework2_1 <- read_twitter_csv("Homework1_1_2.tweets.csv") %>%
  ## Select columns, we are going to use
  select(text,created_at,user_id,screen_name,favorite_count,retweet_count,hashtags) %>%
  ## Transform coding from one format to another #seeingIsBelieving
  mutate(text=iconv(text,from="latin1",to="ascii",sub="byte")) %>%
  ## Crucial transformation, which kept me awake one fun night. Transform dataset from one format to another. Without it the next function doesn't work
  as.data.frame() %>%
  ## Replace emojis with their descriptions. It takes a while and might return some warnings, but you can igonre them.
  FindReplace(Var = "text",
              replaceData = emojis,
              from = "code", to = "description",
              exact = FALSE) %>%
  ## Getting rid of emojis which we were not able to match with description
  mutate(text=str_replace_all(string=text,
                              replacement="",
                              pattern="(<[:alnum:]{2}>)")) %>%
  ## Delete hashtags we used in the querry
  mutate(text=str_replace_all(string=text,
                              replacement="",
                              pattern="(@warriors)|(@knicks)")) %>%
  ## In each row in text column look for phrase containing link and replace it with nothing
  mutate(text=str_replace_all(string=text,
                              pattern="http[[:alnum:][:punct:]]*",
                              replacement = "")) %>%
  ## split words into stems
  unnest_tokens(output=word,
                input=text) %>%
  ## Delete rows with stop words
  anti_join(stop_words) 
  
```

## Compute sentiment

Use bing sentiment dictionary and compute sentiment for your NBA game data set.

*Note:* Use the transformed data however do not load the saved file but use the object which is in environment. In other words you **can not** close RStudio between doing task one and task two from this Homework otherwise a unicorn dies...

*Solution:* Probably nothing to comment.

```{r compute_sentiment}
sentiment <- get_sentiments("bing")

Homework2_2 <- Homework2_1 %>%
  inner_join(sentiment)

write.csv2(Homework2_2,"Homework2_2.csv")
```

## Plot 

Plot how sentiment changed over time aggregating tweets using one hour interval. Explain what might have influenced overall sentiment in your data set.

*Challenging Challenge:* See which words load sentiment categories and delete the ones which load sentiment but should not. Justify why you delete each word.

*Solution:* When I was writing this homework was not expecting it would be that challenging. I mean if I did not make a mistake in the script you probably would not have any problems. I think `Erratum.Rmd` should answer most of your questions. In the script below I aggregated time by one hour interval but you could have done it with the interval you fancied.

```{r plot}
Homework2_2 %>%
  ## Add up words groupped by word and sentiment. Sort the results
  count(word, sentiment, sort = TRUE) %>%
  ## Group words by sentiment
  group_by(sentiment) %>%
  ## Filter ten most frequent words within each sentiment
  top_n(10) %>%
  ## Ungroup
  ungroup() %>%
  ## Reorder words by frequency
  mutate(word = reorder(word, n)) %>%
  ## Plot the chart. Define that words should be on x ax, frequency on y, and sentiment colored
  ggplot(aes(x=word, y=n, fill = sentiment)) +
  ## Get rid of legend
  geom_col(show.legend = FALSE) +
  ## Plot one chart for each sentiment type, and let the scale on y ax differ beetwen them
  facet_wrap(~sentiment, scales = "free_y") +
  ## Name the labs
  labs(y = "Contribution to sentiment",
       x = NULL) +
  ## Flip axis
  coord_flip() +
  ## Define the theme of the chart
  theme_classic()

## I remove word golden because it obiously refers to Golden State Warriors not to anything else.
word <- c("golden")

## Update Data set
Homework2_2 <- Homework2_2 %>%
  anti_join(data_frame(word))

## Draw the plot
Homework2_2 %>%
  ## Choose only positive and negative sentiment
  filter(sentiment %in% c("positive","negative")) %>%
  ## Create new variables
         ## Extract day from the date
  mutate(day=created_at %>% day,
         ## Extract hour from the date
         hour=created_at %>% hour,
         ## Extract minute form the date
         minute=created_at %>% minute) %>%
  ## Create new variable time, which aggregates time by one hour minutes interval
                        ## If minute less than 60 minutes set minutes equals 0
  mutate(time=case_when(minute < 60 ~ paste0("18-01-",day," ",hour,":00:00")),
         ## Convert variable time to date format. Super important
        time=time %>% as_datetime(tz=NULL)) %>%
  ## Plot bar chart. This time I am not defining axis here, because I want to use two different data sets match_events and FACup_sentiment
  ggplot() +
  ## Setting theme of the chart
  theme_classic() +
  ## Define axis, and say that we are interested with proportions not counts
  geom_bar(aes(x=time,fill=sentiment),position="fill") +
  ## Name the labs
  labs(x = NULL, y = NULL,
    title = "Proportion of sentiment on @warriors and @knicks between Jan 22 and Jan 30",
    subtitle = "Tweets counts aggregated using one hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Specify that we do not want to have name of the legend but just types of sentiment
  scale_fill_discrete("")
  
```

# Explanation

The game was held in San Francisco, and we gathered tweets only from California so such a big percentage of negative tweets on a day before the game must be surprising. In the end when you live in California and tweet about NBA you probably support GSW not NYK. Therefore your tweets should be optimistic cause your team is the best in the league and Knicks are not that good even though they have Porzingis. However, probably the reason why there was such a big percentage of negative tweets is that on Jan 20 Warriors lost important game to Rockets. Although, it is still regular season and they have still the best record in the league, the game was important because most likely they are going to meet in the finals of Eastern Conference. DubNation has something to think about because this season in head to head Rockets lead 2-1.

## It is a lot but

Aggregate sentiment by tweets.

```{r agrregate}
#Homework2_3 <- NULL ## replace NULL with solution, otherwise it returns error.

## Save solution
#write.csv2(Homework2_3,"Homework2_3.csv")
```
<!-- CSS styling -->
<style>
    html {
        height: 100%;
        font-size: 62.5%;
    }
    body {
        text-align: justify;
        height: 100%;
        font-size: 1.6em;
        font-family: "Trebuchet MS", "Lucida Grande", "Lucida Sans Unicode", "Lucida Sans", sans-serif;
    }
    h1, h2, h3 {
        text-align: center;
    }
    h4.author, h4.date {
        margin: 0.75em 0 0 0;
        text-align: center;
    }
    h2, h3, h4, h5, h6 {
        margin: 2em 0 1em 0;
    }
    div#header {
        margin: 1em 0 1em 0;
    }
    hr {
        margin: 2em 0 2em 0;
    }
    pre {
        margin-bottom: 2em;
    }
</style>