---
title: "Twitter-3 | More advanced text analysis"
author: "Szymon Talaga, Mikołaj Biesaga, ISS UW"
output:
  html_notebook:
    toc: true
---
```{r global_options, include = FALSE}
# Do not bother with this chunk because it only defines some visual options for other chunks
knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE, include = TRUE, fig.align = "center", fig.height = 2, fig.width = 2
)
```

## What will we do in this script?
Last time we learnt, hopefully, how to do some basic word analysis. More or less we talked about words frequency and sentiment. In this script we are going to do some more advanced things, however they still should be straightforward.

## Beofore loading packages

For some of you loading package `ggrpah` returned error. Below there is a solution to it. You just need to run the code below and everything should be fine.

```{r solution}
#install.packages("remotes")
#library(remotes)
#install_github("cran/viridisLite")
#library(viridisLite)
```

As you probably noticed it is about installing two packages not really linked to ggraph. Without going too much into details you just need to run this chunk of the code once and afterwards you can forget about it.

## Load and install packages

Again we start with installing and loading packages. There is quite a few of them but most of them serve for data manipulation. The new thing is `source("clean_twitter_data.R")`. It is just our custom function written in the other script, which we load into this script.

```{r load_packages}
## Install packages for text analysis
#packages <- c("reshape2","igraph","ggraph","widyr","feather","scales","lubridate","PMCMRplus")
#install.packages(packages)

## Load packages needed in this script
library(rtweet) # for downloading data from Twitter
library(dplyr) # for data transformation
library(magrittr) # for data transformation
library(tidytext) # for text analysing
library(stringr) # for dealing with strings
library(wordcloud) # for basic text visualisation
library(ggplot2) # for graphics
library(DataCombine) # for data transformation
library(reshape2) # for data transformation
library(tidyr) # for data transformation
library(igraph) # for creating graphs
library(ggraph) # for creating graphs
library(widyr) # for ngrams statistics
library(lubridate) # for date transformation
library(feather) # for very light data format
library(PMCMRplus) # for post hoc kruskal-walis test
library(scales) # for scales
source("clean_twitter_data.R") # load our custom cleaning function
data("stop_words") # load data frame with stop words.
```

## Search/Stream Tweets

However, first things first, we need some data to process. This time we will start with tweets from NBA, NFL, MLS and NHL official Twitter accounts. The code below would download the tweets, but to save time we have already done it at home. So, like in cooking shows we will load the data from the csv file we prepared before.

You probably realized that when you use function `save_as_csv()` from `rtweet` it creates not one but two csv files. One is a data frame with tweets as records, and the other one with profiles of users who tweetted.

```{r search_tweets}
# ## Querry we run
# NFL_NBA_MLS_NHL <- get_timelines(c("NFL","NBA","NHL","MLS"),
#                           n=3200,
#                           parse=TRUE)
# ## Save to csv
# save_as_csv(NFL_NBA_MLS_NHL, "NFL_NBA_MLA_NHL.csv")
```

## Transform data

Last time we wanted to show you data set transformation step by step. However, since we are going to use more or less the same transformations on quite a few data sets, we put them in one function - `clean_twitter_data()`. It takes as an argument raw data frame from Twitter, and returns data frame with tweet, creation time, unique tweets id, unique users name, favorite count, retweet count, hashtags, logical variable if the tweet was a retweet, and logical variable if the tweet was a quote. The text of the tweet is almost ready for unnesting tokens because it does not contain links and emojis are translated, the only thing left to do is to remove hashtags used in the query if there were any. 

```{r transform_data}
# ## Clean the data with the use of our cleaning function
# NFL_NBA_MLS_NHL <- read_twitter_csv("NFL_NBA_MLS_NHL.tweets.csv") %>%
#   clean_twitter_data()
# 
# ## Save the result of the funciton because it takes a while
# write.csv2(NFL_NBA_MLS_NHL,"NFL_NBA_MLS_NHL.csv")
```

## Term Frequency and Inverse Term Frequency

One of the central concerns in text analysis is frequency of words in the document. Such a simple measure tells us more or less what the text is about. But, does it? Usually the most common words are stop words, which we have already learnt how to delete. With just one document or tweets on the same topic (hashtag or whatever we put in our query) word frequency without stop words should be enough, however what to do if we want to compare multiple documents like in NFL_NBA_MLS_NHL data set?

We have a collection of tweets from NFL, NBA, MLS and NHL official Twitter accounts and we want to know the most important words for each source. In other words we want to look for words which are unique for one of the sources. Therefore, we will compute term frequency inverse document frequency (tf-idf), which tells us how important for a document a given word is. Basically, it multiplies frequency of a given word (tf) times weights (idf).

$$idf(word)=ln(\frac{n_{documents}}{n_{document\ contatining\ word}})$$ 
where $n_{documents}$ is number of documents, and $n_{number\ containing\ word}$ - number of documents containing word.

### Data transformation for tf-idf

The idea of tf-idf is to decrease importance of the common words which occur in all accounts (NFL, NBA, MLS, and NHL) tweets and increase importance of the words which are specific for one or some of them.

```{r tf_idf_data_transformation}
## Unnest tokens
NFL_NBA_MLS_NHL_words <- read.csv2("NFL_NBA_MLS_NHL.csv") %>%
  ## Convert format of the tweet from one to another. It is needed because we saved our file with the use of write.csv2 function.
  mutate(text=as.character(text)) %>%
  ## Unnest tokens
  unnest_tokens(input=text,
                output=word) %>%
  ## Delete stop words
  anti_join(stop_words)

## Count total number of words for each timeline
total_words <- NFL_NBA_MLS_NHL_words %>%
  ## Count number of words
  count(screen_name,word,sort=TRUE) %>%
  ## Ungroup
  ungroup() %>%
  ## Group by screen name
  group_by(screen_name) %>%
  ## Return sum of words for each account
  summarise(total=sum(n))

## Count words
NFL_NBA_MLS_NHL_count <- NFL_NBA_MLS_NHL_words %>%
  ## Count words
  count(screen_name,word,sort=TRUE) %>%
  ## Ungroup
  ungroup() %>%
  ## Add total number of words to each word by joining by screen names
  left_join(total_words)
```

### Compute tf-idf

So computing tf-idf is quite easy, because there is a function `bind_tf_idf()` which does it for us. Thanks to the chart below we can identify words, which are somehow specific for each of the accounts.

The second graph shows words which are common in NFL and NBA tweets. If the word is below red line it appears more often in NFL tweets, while when over in NBA tweets. You can try to make similar plots for all combinations in your data set.

```{r tf_idf_visualisation}
## Compute term frequency inverse document frequency
NFL_NBA_MLS_NHL_count %>%
  bind_tf_idf(word, screen_name, n) %>%
  ## Arrange it in decreasing order
  arrange(desc(tf_idf))

## See specific words for all accounts
NFL_NBA_MLS_NHL_count %>%
  ## Compute term frequency inverse document frequency
  bind_tf_idf(word, screen_name, n) %>%
  ## Arrange the table in order of decreasing tf-idf
  arrange(desc(tf_idf)) %>%
  ## Convert words from one format to another.
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  ## Group by account
  group_by(screen_name) %>% 
  ## Pick top 20 from each account
  top_n(20) %>% 
  ## Ungroup
  ungroup %>%
  ## Plot the graph with words and tf-idf on axis and account as color
  ggplot(aes(word, tf_idf, fill = screen_name)) +
  ## Plot bars without legend
  geom_col(show.legend = FALSE) +
  ## Name only y ax
  labs(x = NULL, y = "tf-idf") +
  ## Plot four graphs in each different account, two in each column and make it possible to have different values (words) on scales 
  facet_wrap(~screen_name, ncol = 2, scales = "free") +
  ## Flip the axis
  coord_flip() +
  ## Set theme
  theme_classic() +
  ## Put the title and label axis
  labs(title = "The most influential words specific for MLS, NBA, NFL and NHL Twitter accounts",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet")

## Compare words which appear in in NFL and NBA accounts.
NFL_NBA_MLS_NHL_count %>%
  ## compute tf-idf
  bind_tf_idf(word, screen_name, n) %>%
  ## Arrange the table in order of decreasing tf-idf
  arrange(desc(tf_idf)) %>%
  ## Select columns, screen name, word and word frequency
  select(screen_name, word, tf) %>% 
  ## Convert the data from lonf format to wide format
  spread(screen_name, tf) %>%
  ## Arrange the table in order of decreasing NFL and NBA
  arrange(NFL, NBA) %>%
  ## Get rid off words which do not appear in NFL and NBA accounts
  filter(!is.na(NBA) & !is.na(NFL)) %>%
  ## Get rid of numbers
  filter(!str_detect(word, "\\d")) %>%
  ## Plot the graph, speicfy the axis
  ggplot(aes(NFL, NBA)) +
  ## Draw words instead of points
  geom_text(aes(label = word)) +
  ## Convert scales from logarithm to percents and set limits from .001 to .5
  scale_x_log10(labels = percent_format(),limits=c(0.001,.5)) +
  scale_y_log10(labels = percent_format(),limits=c(0.001,.5)) +
  ## Draw a diagonal line
  geom_abline(color = "red") +
  ## Set the theme
  theme_classic() +
  ## Name axis
  labs(title = "Probability of common words between NFL and NBA accounts to appear in their tweets",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet")
```

### Application

The tf-idf transformation is usually used instead of stop words dictionary. Words such "a, an and the" appear usually in all documents, so tf-idf for them is equal 0 (since $idf(word)=ln(1)=0 => tf(word) \times 0 = 0$). The advantage of such solution is that you do not need to update your stop words dictionary for each collection of words. Disadvantage, of course, is that you need to have at least two documents.

The other use might be creating a dictionary. If you know that some tweets are in one category and other in the second you can easily find words which are specific for both categories. You just need to to find words with tf-idf value smaller than one. It is shown below how to create a dictionary.

#### Creating dictionary

You need to find words with the highest idf value because of the logarithm properties. In MLS_NHL_NBA_NHL example idf for words appearing only in one Twitter account would take value $1.386294$, for two - $0.6931472$, for three $0.2876821$, and for four $0$. The code below should guide you how to do it in practice

```{r creating_dicitonary}
## Take data set with words count
NFLS_NBA_MLS_NHL_dictionary <- NFL_NBA_MLS_NHL_count %>%
  ## Compute tf-idf 
  bind_tf_idf(word, screen_name, n) %>%
  ## Filter only maximum values of tf_idf value
  filter(idf==max(idf)) %>%
  ## Select only columns needed in dictionary, it means word and name of the account
  select(screen_name,word) %>%
  ## Change screen_name column's name to organization
  rename(organization=screen_name)
```

Probably this dictionary is a bit dull because who would need dictionary to categorize people's tweets in terms of organization they talk about... However, this method is quite simple and effective in terms of categorizing tweets. 

## Simple models of sentiment

The last graph in previous section answers the most basic question which account is more probable to tweet with specific words. It is more or less boring question and easy to answer for all accounts (you might try to answer it at home). What we will do here is something more interesting. We are going to predict what is more probable NBA account tweeting something positive or negative?

We need to admit that the approach we are going to take stands kind of in contradiction with what we have been talking about on Fridays. You probably remember we said that with Big Data you only need to use descriptive statistics or correlations. You are actually talking about population so there is no point of estimating means or any other statistics cause you have the truth parameters. In theory, yes that is still true, but in our example not necessary because we are still talking about samples, therefore we are using approach you have already known. We would say that it is hard to say where is the cutting point of using descriptive statistics, you need to decide about it yourself.

### Visualisation

Before we start let's look at graphs. The charts below show what are the top 3 most probable words from each sentiment category to appear in tweets from all sources. Some of the words appear only in one of the accounts, therefore not all have four probability bars.

```{r simple_model}
## Count total number of tweets from each source
number_of_tweets <- read.csv2("NFL_NBA_MLS_NHL.csv") %>%
  ## Group by screen name
  group_by(screen_name) %$%
  ## Compute frequency
  table(screen_name) %>%
  ## Convert the format
  as_tibble() %>%
  ## Rename variable
  rename(tweets_nr=n)

## Get sentiment
sentiment <- get_sentiments("nrc")

## Visualise words
NFL_NBA_MLS_NHL_count %>%
  ## Join total number of tweets from each source to the count data frame
  left_join(number_of_tweets) %>%
  ## Compute probability
  mutate(prob=n/tweets_nr) %>%
  ## Compute sentiment
  inner_join(sentiment) %>%
  ## Group by sentiment category and screen name
  group_by(sentiment,screen_name) %>%
  ## Pick words with top 5 probabilities for each screen name and sentiment category
  top_n(3,wt=prob) %>%
  ## Ungroup
  ungroup() %>%
  ## Reorder words so the ones with highest probability are first
  mutate(word = reorder(word, prob)) %>%
  ## Plot chart. Define axis and colour
  ggplot(aes(word,(prob),fill=screen_name)) +
  ## Draw separate plot for each sentiment category. Allow to have different words for each sentimetn category
  facet_wrap(~sentiment, scales="free_y") +
  ## Set position of the bars
  geom_col(position="dodge") +
  ## Set theme
  theme_classic() +
  ## Flip axis
  coord_flip() +
  ## Title and label axis
  labs(x = "Probability", y = NULL,
    title = "Probability of words appearing in tweets which load sentiment categories the most",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Specify names in the legend, and change default colors to red and blue
  scale_fill_discrete("")
```

### Simple models

If you look at the charts you will notice, obviously, that some of the words appear in tweets from all sources and some do not. Therefore, we can either limit words to the ones which were tweeted by all accounts or check if there are significant differences between probabilities of tweeting word with certain sentiment between sources. In other words what we are going to do now is to compare probabilities of using positive or negative word by NBA and NFL account (you can try to do MLS and NHL yourself). To do so we will use Kruskall-Wallis Rank Test. It is not the best approach we can use but for our purposes optimal in terms of how easy it is to compute. For more advanced things consider for example quantile regression (read documentation for package `quantreg`).

Before we start we need to admit to something, we tried it at home and it did not work out as good as it should. Think about it what we want to comapre. Can we predict how big the differences will be? Probably really small, not only because of their nature but mainly because probabilities range which is from 0 to 1. It would be much better if we could only stretch a bit this scale. Actually, yes we can do that using Logit trasnformation. It is really usefull concept and quite simple.

#### Logit transformation

Imagine you have logical variable which takes value 1 if word "quite" appears in a tweet and 0 when it does not. Now you have let say 100 tweets from 100 Brits and 100 Americans. We can easily compute probabiliteis of "quite" appearing in person's tweets. And in terms of comparing these two groups, it would be enough, especially with Kruskal-Walis Sum Rank Test because it would just rank the results, compare two distributions and say if they are distinctive enough. In other words the values does not matter for this test, only order does. However, small range of results in terms of visualisation might be a problem. Therefore, we can spread the scale, here, comes Logit transformation, which is a standard solution for this kind of problems (spreading binary scale not visualisation, for more on this read about Logit regression). We can easily transform probablity into odds - $$\frac{probability\ of\ succes}{probability\ of\ failure}$$ which returns values from 0 to $\infty$. Afterwards, if we take the natural logarithm of odds we will end up with continous variable, which returns negative values when probability of succes is smaller than probability of failure, and positive when success is more probable than failure. Thanks to such transformation we transformed logical variable into contionous which is spread from $-\infty$ to $\infty$, but we did not change the order.

#### NFL

First, we will check if there is a difference between probability of tweets from NFL having positive and negative sentiment. To do so we will just perform Kruskal-Wallis Sum Rank Test. In other words we will check if results for positive and negative categories belong to the same population in terms of probability.

```{r simple_models_NFL_positive_negative}
## Is there difference positve and negative word appearing in tweet about NFL
NFL_pos_neg <- NFL_NBA_MLS_NHL_count %>%
  ## Join total number of tweets from each source to the count data frame
  left_join(number_of_tweets) %>%
  ## Compute probability and logit
  mutate(prob=n/tweets_nr,
         logit=log(n/tweets_nr)/(1-(n/tweets_nr))) %>%
  ## Compute sentiment
  inner_join(sentiment) %>%
  ## Filter for NFL
  filter(screen_name=="NFL") %>%
  ## Filter positive and negtive sentiment only
  filter(sentiment %in% c("positive","negative"))


## For some reason with pipeline this Kruskal-Wallis did not work. Now it returns right results. Therefore I use a different approach of relating to columns of a data frame. Function with() executes second argument within data set which is the first argument. So in the sense it is really similar to pipelines.

## Simple Kruskall-Wallis Sum Rank Test on probabilities
with(NFL_pos_neg,
     kruskalTest(prob~as.factor(sentiment)))

## Simple Kruskal-Wallis Sum Rank Test on logit scale 
with(NFL_pos_neg,
     kruskalTest(prob~as.factor(sentiment)))

## Visualisation of probabilities
NFL_pos_neg %>%
  ## Define axis
  ggplot(aes(x=sentiment,fill=sentiment,y=prob))+
  ## Create boxplots, without showing legend
  geom_boxplot(show.legend = FALSE) +
  ## Set the theme
  theme_classic() +
  ## Name axis
  labs(x = NULL, y = "Probability",
    title = "Probablity boxplots of negative and positive sentiment",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Specify names in the legend
  scale_fill_discrete("")

## Visualisation of probabilities on logit scale
NFL_pos_neg %>%
  ## Define axis
  ggplot(aes(x=sentiment,fill=sentiment,y=logit))+
  ## Create boxplots, without showing legend
  geom_boxplot(show.legend = FALSE) +
  ## Set the theme
  theme_classic() +
  ## Name axis
  labs(x = NULL, y = "Probability (on logit scale)",
    title = "Probablity boxplots of negative and positive sentiment",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Specify names in the legend
  scale_fill_discrete("")
```

#### NBA

Second, we will compute the same for different sentiment for NBA.
```{r simple_models_NBA_other_sentiment}
NBA_other_sentiment <- NFL_NBA_MLS_NHL_count %>%
  ## Join total number of tweets from each source to the count data frame
  left_join(number_of_tweets) %>%
  ## Compute probabilites
  mutate(prob=n/tweets_nr,
         logit=log(n/tweets_nr)/(1-(n/tweets_nr))) %>%
  ## Compute sentiment
  inner_join(sentiment) %>%
  ## Filter for NFL
  filter(screen_name=="NBA") %>%
  ## Filter positive and negtive sentiment only
  filter(!sentiment %in% c("positive","negative"))

## For some reason with pipeline this Kruskal-Wallis did not work. Now it returns right results. Therefore, I use a different approach of relating to columns of a data frame. Function with() executes second argument within data set which is the first argument. So in the sense it is really similar to pipelines.

## Simple Kruskall-Wallis Sum Rank Test
with(NBA_other_sentiment,
     kruskalTest(prob~as.factor(sentiment)))
## Pairwise comparisons using Dunn's all-pairs test, which should be cool with unequal samples. Now that works too.
with(NBA_other_sentiment,
     kwAllPairsDunnTest(NBA_other_sentiment$logit~as.factor(NBA_other_sentiment$sentiment)))


## Visualisation
NBA_other_sentiment %>%
  ## Define axis
  ggplot(aes(x=sentiment,fill=sentiment,y=logit)) +
  ## Create boxplots, without showing legend
  geom_boxplot(show.legend = FALSE) +
  ## Set theme
  theme_classic() +
  ## Name axis
  labs(x = NULL, y = "Probability (on logit scale)",
    title = "Probablity boxplots of sentiment's different categories",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Specify names in the legend, and change default colors to red and blue
  scale_fill_discrete("")
```

## Bigrams

Before, we were focused on words (actually stems...) and how to compute sentiment analysis basing on them. This time we are going to shift our area of interest from words to n-grams (combination of n words). In other words we are going to analyse co-occurrence of words and plot them into networks.

## Search/Stream Tweets

We need new data, because we want have more than four distinctive users. Therefore, we are going to search for a new tweets. We are not sure if you are not tired with sport but we are not. Let's talk about Australian Open now. We are preparing this script in the beginning of the second week so we can still believe Federer is going to win his 20th Grand Slam Title #believe.

```{r search_tweets2}
# ## Search for tweets
# AO <- search("#AusOpen",
#              n=18000,
#              type="recent",
#              include_rts=FALSE,
#              lang="en")
# 
# save_as_csv(AO,"AO.csv")
```

## Transform data

We are going to use again our custom function `clean_twitter_data()` to clean the original data frame. Since the processing of the data set takes a while we save the result in csv format.

```{r transforom_data2}
# ## Read the orginal data set
# read_twitter_csv("AO.tweets.csv") %>%
#   ## Clean the data
#   clean_twitter_data() %>%
#   ## Delete hashtags we used in the querry
#   mutate(text=str_replace_all(string=text,
#                               replacement="",
#                               pattern="(#AusOpen)")) %>%
#   ## Save it as csv
#   write.csv2("AO.csv")

## Transformation to bigrams
AO_bigrams <- read.csv2("AO.csv") %>%
  ## Split tweets into bigrams
  unnest_tokens(output=bigram,
                input=text,
                token="ngrams",
                n=2)
```

With bigrams we can obviously do the same type of analysis as with single words. It means we can compute tf-idf statistics, probabilities or create simple models. However, as the procedure is really similar we will skip it here (you can try it at home).

## Sentiment analysisc with bigrams

The problem with sentiment analysis as we learnt so far is that it does not take into account negations. We just assigned either category or score to words which repeated in our sentiment dictionary. However, in language it does not work that easy, for example pair of words "not happy" does not necessary load positive sentiment, to say at least. We can easily find the words which load the wrong sentiment.

```{r bigram_sentiment}
## Load sentiment dictionary
sentiment <- get_sentiments("nrc")
## Negation words
negations <- c("not","never","no","without")

## Load bigrams
AO_bigrams %>%
  ## Separate words
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  ## Compute sentiment for second word
  inner_join(sentiment,by=c(word2 = "word")) %>%
  ## Add "-" before sentiment category when the secon words is proceded by negative word
  mutate(sentiment=if_else(word1 %in% negations,paste0("-",sentiment),sentiment))
```

As you can see finding words which load wrong sentiment category is really easy. The harder part is to decide what to do with them. We can either delete them or try to recode them. It is up to you to justify which approach you are going to take. Below we show how to recode sentiment from one category to another and plot the results. The example shows it only with positive negative sentiment because with specific sentiment categories it is even harder to decide which category "never trust" loads.

```{r recode_bigram_sentiment}
## Load sentiment dictionary
sentiment <- get_sentiments("nrc")
## Negation words
negations <- c("not","never","no","without")

## Load bigrams
AO_bigrams %>%
  ## Separate words
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  ## Compute sentiment for second word
  inner_join(sentiment,by=c(word2 = "word")) %>%
  ## Add "-" before sentiment category when the secon words is proceded by negative word
  mutate(sentiment=if_else(word1 %in% negations,paste0("-",sentiment),sentiment)) %>%
  ## Recode -positive and -negative to negative and positive
  mutate(sentiment= case_when(sentiment=="-positive" ~ "negative",
                              sentiment=="-negative" ~ "positive",
                              TRUE ~ sentiment)) %>%
  ## Filter only positive and negative sentiment
  filter(sentiment %in% c("positive","negative")) %>%
  ## Filter only words which are proceed by negations
  filter(word1 %in% negations) %>%
  ## Count words
  count(word2, sentiment, sort = TRUE) %>%
  ## Group words by sentiment
  group_by(sentiment) %>%
  ## Filter ten most frequent words within each sentiment
  top_n(15) %>%
  ## Ungroup
  ungroup() %>%
  ## Reorder words by frequency
  mutate(word2 = reorder(word2, n)) %>%
  ## Plot the chart. Define that words should be on x ax, frequency on y, and sentiment colored
  ggplot(aes(x=word2, y=n, fill = sentiment)) +
  ## Get rid of legend
  geom_col(show.legend = FALSE) +
  ## Plot one chart for each sentiment type, and let the scale on y ax differ beetwen them
  facet_wrap(~sentiment, scales = "free_y") +
  ## Name the labs
  labs(y = "Contribution to sentiment",
       x = NULL,
       title = "Words proceeded by negations contribution to positive and negative sentiment",
    subtitle = "",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  ## Flip axis
  coord_flip() +
  ## Define the theme of the chart
  theme_classic()

```

## Visualising bigrams as network

We can easily find words which connects two words by visualizing bigrams as networks. It means they co-occurred.

```{r bigram_networks}
## Create a network from bigrams
AO_bigrams %>%
  # Separate bigrams into two words
  separate(bigram,
           c("word1","word2"),
           sep=" ") %>%
  ## Filter stop words in word1
  filter(!word1 %in% stop_words$word) %>%
  ## Filter stop words in word2
  filter(!word2 %in% stop_words$word) %>%
  #filter(word1 %in% c("federer","nadal","roger","rafael","rafa") | word2 %in% c("roger","rafa","rafael","federer","nadal")) %>%
  ## Count words
  count(word1,word2, sort=TRUE) %>%
  ## Filter words which are not digits and have frequency above 40
  filter(n>40,
         !str_detect(word1, "\\d"),
         !str_detect(word2, "\\d")) %>%
  ## Convert data frame into graph data frame with edges
  graph_from_data_frame() %>%
  ## Plot graph
  ggraph(layout = "fr") +
  ## Define edge. Its length, thicknes, and shape
  geom_edge_link(aes(edge_alpha = n),arrow=arrow(type="open",length=unit(.1,"inches")), show.legend = FALSE) +
  ## Define node
  geom_node_point() +
  ## Define label of node
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  ## Set the theme
  theme_void()
```

With Australian Open data network is quite boring because it returns more or less names of tennis players. It is because we set to filter only nodes with more than 40 appearances in the data set. Changing it to a lower number would be one way of looking for something interesting, however if we do that the graph is too big and hard to read. Therefore, we will pick just part of the big network and have a closer look at connections between The Greatest of All Times His Majesty King Roger Federer and his biggest rival Current Number One Rafael Nadal. They were meant to meet in the final but we all know how it ended up.

```{r bigram_network2}
## Create a network from bigrams
AO_bigrams %>%
  # Separate bigrams into two words
  separate(bigram,
           c("word1","word2"),
           sep=" ") %>%
  ## Filter stop words in word1
  filter(!word1 %in% stop_words$word) %>%
  ## Filter stop words in word2
  filter(!word2 %in% stop_words$word) %>%
  ## Select only Roger Federer and Rafael Nadal as nodes
  filter(word1 %in% c("federer","nadal","roger","rafael","rafa") | word2 %in% c("roger","rafa","rafael","federer","nadal")) %>%
  ## Count words
  count(word1,word2, sort=TRUE) %>%
  ## Filter words which are not digits and have frequency above 2
  filter(n>2,
         !str_detect(word1, "\\d"),
         !str_detect(word2, "\\d")) %>%
  ## Convert data frame into graph data frame with edges
  graph_from_data_frame() %>%
  ## Plot graph
  ggraph(layout = "fr") +
  ## Define edge. Its length, thicknes, and shape
  geom_edge_link(aes(edge_alpha = n),arrow=arrow(type="open",length=unit(.1,"inches")), show.legend = FALSE) +
  ## Define node
  geom_node_point() +
  ## Define label of node
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  ## Set the theme
  theme_void()
```

The network above is somehow more interesting but if you know something about tennis you probably do not learn anything new from it.

## Pairwise correlation

Thanks to last networks we were able to see words which connect Roger Federer and Rafael Nadal, however it lacked a time span. Of course we can easily imagine creating such a network aggregating data by hours or days, but it would be time consuming and also we would have to know something about networks to compare them. Here, we will use pairwise correlation to compute something more or less similar. We will try to answer the question how co-occurence of words connected to Roger Federer and Rafael Nadal changed hour after hour and day after day. Important notion is that computation will take time and generate huge file unless you filter data carefully #beenThere.

We are going to compute *phi coeffcient*, a common measure for binary data. It just tells you how often certain words appear together, and separately. 

$$\phi=\frac{n_{11}n_{00}-n_{10}n_{01}}{\sqrt{n_{1_0}n_{1_1}n_{2_0}n_{2_1}}}$$
where:
$n_{11}$ is number of documents where both words are present
$n_{00}$ is number of documents where neither of words are present
$n_{10}$ is number of documents where first word is present
$n_{01}$ is number of documents where second words are present
$n_{1_1}$ is a sum of $n_{10}$ and $n_{11}$
$n_{2_1}$ is a sum of $n_{01}$ and $n_{11}$
$n_{1_0}$ is a sum of $n_{10}$ and $n_{00}$
$n_{2_0}$ is a sum of $n_{01}$ and $n_{00}$

The formula you see above is just here to show you how to compute it with paper and pencil, however you do not have to think about it too much, because there is a function which will do all the computations for us. Interpretation of this coefficient is quite simple because like every correlation coefficient $\phi \in [-1,1]$, therefore if it is negative the words occur more often separately than together.

```{r pairwise_correlation}
## Compute pairwise corelations
AO_bigrams %>%
  ## Transform from bigrams to words
  unnest_tokens(input=bigram,
                output=word) %>%
  ## Remove digits
  filter(!str_detect(word, "\\d")) %>%
  ## Remove stop words
  filter(!word %in% stop_words$word) %>%
  ## Filter words we want to check cooccurence
  filter(word %in% c("federer","nadal","roger","rafael","rafa")) %>%
  ## Transform date from one format to another
  mutate(created_at=created_at %>% as.character() %>% ymd_hms(),
         ## Create variable with day
         day=created_at %>% as.character() %>% ymd_hms() %>% day,
         ## Create variable with hour
         hour=created_at %>% as.character() %>% ymd_hms() %>% hour) %>%
  ## Compute corelations 
  pairwise_cor(word,day,hour,sort=FALSE) %>%
  ## Save the file in quite fast format because files might be huge here
  write_feather("AO_cor")

## Read the file
read_feather("AO_cor") %>% 
  ## Reorder item2 by correlation
  mutate(item2 = reorder(item2, correlation)) %>%
  ## Plot the graph with words as y, correlation as x, and collored item1
  ggplot(aes(item2, correlation, fill=item1)) +
  ## Set bars to display correlation instead of frequency
  geom_bar(stat = "identity", show.legend = FALSE) +
  ## Plot five graphs in each different correlations with different word and make it possible to have different scales
  facet_wrap(~ item1, scales = "free") +
  ## Flip axis
  coord_flip() +
  ## Set theme
  theme_classic() +
  ## Title and axis labels
  labs(y = NULL,
       x = NULL,
       title = "Does words Federer, Nadal, Rafa, Rafael and Roger occur more often together or separetly?",
    subtitle = "\nData aggregated by tweets",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet") +
  scale_color_discrete("",labels=c("Rafael Nadal","Roger Federer"))
```

We can also visualize correlation as networks. The more dark the edge is the more positive correlation is.

```{r pairwise_network}
read_feather("AO_cor") %>%
  graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(edge_alpha = correlation), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), repel = TRUE) +
  theme_void()
```

## Conclusions

There is much more about text analysis but we would say that in the scripts we went through there are same basics. They were not meant to teach you everything but give some simple tools you can develop yourself. For more on this topics we recommend book by Julia Silge and David Robinson. You can find it for free here
https://www.tidytextmining.com/sentiment.html

<!-- CSS styling -->
<style>
    html {
        height: 100%;
        font-size: 62.5%;
    }
    body {
        text-align: justify;
        height: 100%;
        font-size: 1.6em;
        font-family: "Trebuchet MS", "Lucida Grande", "Lucida Sans Unicode", "Lucida Sans", sans-serif;
    }
    h1, h2, h3 {
        text-align: center;
    }
    h4.author, h4.date {
        margin: 0.75em 0 0 0;
        text-align: center;
    }
    h2, h3, h4, h5, h6 {
        margin: 2em 0 1em 0;
    }
    div#header {
        margin: 1em 0 1em 0;
    }
    hr {
        margin: 2em 0 2em 0;
    }
    pre {
        margin-bottom: 2em;
    }
</style>
