---
title: "Homework-1 | Basic functions"
author: "Szymon Talaga, Mikołaj Biesaga, ISS UW"
output:
  html_notebook:
    toc: true
---

```{r global_options, include = FALSE}
# Do not bother with this chunk because it only defines some visual options for other chunks
knitr::opts_chunk$set(
    echo = TRUE, warning = FALSE, message = FALSE, include = TRUE, fig.align = "center", fig.height = 3, fig.width = 3
)
```

```{r load_packages}
## Load packages needed in this script
library(rtweet) # for downloading data from Twitter
library(dplyr) # for data transformation
library(magrittr) # for data transformation
library(tidytext) # for text analysing
library(stringr) # for dealing with strings
library(wordcloud) # for basic text visualisation
library(ggplot2) # for graphics
library(DataCombine) # for data transformation
library(reshape2) # for data transformation
```

## Search tweets

Use `search_tweets()` function to look for at least 1000 tweets about NBA game of your choice. Limit them only to the state in which the game was played. Include retweets.

*Hint:* Remember about `lookup_coords()` function.

```{r search_tweets}
Homework1_1 <- ## put solution here

## Save the data set
Homework1_1 %>%
  save_as_csv("Homework1_1.csv")
```

## Plot

Plot frequency of original tweets and retweets. Aggregate tweets by 45 minutes.

```{r plot}

```

## Get timeline

Download home timeline of Serena Williams.

*Hint:* User timeline consists of tweets tweetted only by a given user, while in home timeline are tweets posted by accounts followed by a user.

```{r timeline}
Homework1_2 <- ## put solution here
  
## Save timeline
Homework1_2 %>%
  save_as_csv("Homework1_2.csv")
```

<!-- CSS styling -->
<style>
    html {
        height: 100%;
        font-size: 62.5%;
    }
    body {
        text-align: justify;
        height: 100%;
        font-size: 1.6em;
        font-family: "Trebuchet MS", "Lucida Grande", "Lucida Sans Unicode", "Lucida Sans", sans-serif;
    }
    h1, h2, h3 {
        text-align: center;
    }
    h4.author, h4.date {
        margin: 0.75em 0 0 0;
        text-align: center;
    }
    h2, h3, h4, h5, h6 {
        margin: 2em 0 1em 0;
    }
    div#header {
        margin: 1em 0 1em 0;
    }
    hr {
        margin: 2em 0 2em 0;
    }
    pre {
        margin-bottom: 2em;
    }
</style>